Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic

### 2020-05-16 papers/main.tex
plots and tables

\graphicspath{{./../../plots/}}
\newcommand{\real}{\text{real}}

\usepackage{booktabs}
\renewcommand{\arraystretch}{1.2}

@@

Neural Networks (NN) have proven to perform exceptionally well at function
approximation tasks\todo{cite universal approx}. This great approximation
performance unfortunately comes at the cost of generalization beyond the
training domain\todo{cite something?}.  The inability to generalize to unseen
inputs is a fundamental problem that hints at a lack of \emph{understanding} of
the given task. The model merely memorizes the seen inputs and fails to
abstract the true learning task.
This can be demonstrated by training a traditional, dense NN to approximate
three functions
\begin{align}
  \label{eq:approx_tasks}
  f(x) = e^x, && g(x) = \log(x), && h(x) = \sin(x)
\end{align}

\begin{figure}
  \centering
  \input{../plots/exp_log_sin/dense_exp.tex}
  \caption{}%
  \label{fig:}
\end{figure}

Neural Arithmetic Units aim to overcome this problem with units that are able
to represent simple arithmetic operations exactly. By composition of these
units it becomes possible to learn e.g. exponentials, logarithms, and power
functions. This promises to improve on the extrapolation capabilities of NNs
even on tasks that are beyond artificial arithmetic tasks such as learning
multiplication, or a certain power function \todo{cite some examples}.
\todo{mention ODEs as use case}

>>>>

% figures
\usepackage{tikz}
\usetikzlibrary{arrows,backgrounds,positioning,intersections}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{polar}
\usepgfplotslibrary{smithchart}
\usepgfplotslibrary{statistics}
\usepgfplotslibrary{dateplot}
\graphicspath{{./../../plots/}}
\newcommand{\real}{\text{real}}

% tables
\usepackage{booktabs}
\renewcommand{\arraystretch}{1.2}

@@

Numbers and simple algebra are essential not only to human intelligence but also
to the survival of many other
species~\citep{dehaene_number_2011,gallistel_finding_2018}.  This can be taken
as a hint that arithmetic is an important ingredient to a successful,
intelligent agent.  State of the art neural networks are capable of learning
simple arithmetic, but they fail to extrapolate beyond the ranges seen during
training~\citep{suzgun_evaluating_2018,lake_generalization_2018}.
The inability to generalize to unseen inputs is a fundamental problem that
hints at a lack of \emph{understanding} of the given task. The model merely
memorizes the seen inputs and fails to abstract the true learning task.
The failure of numerical extrapolation on simple arithmetic tasks has been shown
by~\cite{trask_neural_2018},
who also introduce a new class of \emph{Neural Arithmetic Units}
that show exceptional extrapolation performance on most arithmetic tasks.
...now explain drawbacks of NALU and NMU...
...we introduce blah...

  This
can be demonstrated by training a traditional, dense NN to approximate three
functions
\begin{align}
  \label{eq:approx_tasks}
  f(x) = e^x, && g(x) = \log(x), && h(x) = \sin(x)
\end{align}

\begin{figure}
  \centering
  \input{../plots/exp_log_sin/gatednpux_exp.tikz}
  \caption{}%
  \label{fig:}
\end{figure}

Neural Arithmetic Units aim to overcome this problem with units that are able
to represent simple arithmetic operations exactly. By composition of these
units it becomes possible to learn e.g. exponentials, logarithms, and power
functions. This promises to improve on the extrapolation capabilities of NNs
even on tasks that are beyond artificial arithmetic tasks such as learning
multiplication, or a certain power function \todo{cite some examples}.
\todo{mention ODEs as use case}
\todo{mention explainability}
